---
title: "eccc 2014-17 projects"
output:
  word_document:
    reference_docx: ../styles/GrantSummary.docx
---
**Last updated: `r format(Sys.Date(), "%B %e, %Y")`**

``` {r setup, echo=F, message=F, warning=F}
require(knitr)
opts_knit$set(root.dir = '..')
```

``` {r startup, echo=F, warning=F, message=F}
rm(list=ls())
require(ProjectTemplate)
load.project()
```

###### Projects with ECCC 2014-17 listed on PROJECTs page
``` {r, echo=T}
ecprojs <- data.frame(PROJECT=projs$Project[grep("ECCC 2014-17", projs$Grants)], PROJECTpage="yes")
```

###### Projects assigned to an ECCC 2014-17 grant statement on GRANT INFO page
``` {r, echo=T}
promprojs <- data.frame(PROJECT=bamGrantInfo$Project[bamGrantInfo$Grant %in% "ECCC 2014-17"], GRANTINFOpage="yes")
```

###### Table of both
``` {r echo=F}
myprojs <- merge(ecprojs, promprojs, by="PROJECT", all=T)
myprojs <- myprojs[!duplicated(myprojs),]
```

`r kable(myprojs)`


# ECCC 2014-17 grant "promises"
``` {r echo=F}
ecproms <- bamGrantInfo[bamGrantInfo$Grant %in% "ECCC 2014-17",]
ecproms$Heading.Lvl1 <- factor(ecproms$Heading.Lvl1)
ecpromss <- split(ecproms, ecproms$Heading.Lvl1.Order)

biglist <- lapply(ecpromss, function(x) {
  y <- x[order(x$Heading.Lvl2.Order),]
  data.frame(Project=y$Project, WorkplanText=y$GrantStatement, Deliverable=y$promisedDeliverable, Status=" ", Explanation=" ")
})
```

# `r unique(ecpromss[[1]]$Heading.Lvl1)`

`r kable(biglist[1], row.names=F)`


# `r unique(ecpromss[[2]]$Heading.Lvl1)`

`r kable(biglist[2], row.names=F)`

# `r unique(ecpromss[[3]]$Heading.Lvl1)`

`r kable(biglist[3], row.names=F)`

# `r unique(ecpromss[[4]]$Heading.Lvl1)`

`r kable(biglist[4], row.names=F)`

# `r unique(ecpromss[[5]]$Heading.Lvl1)`

`r kable(biglist[5], row.names=F)`

# `r unique(ecpromss[[6]]$Heading.Lvl1)`

`r kable(biglist[6], row.names=F)`

# `r unique(ecpromss[[7]]$Heading.Lvl1)`

`r kable(biglist[7], row.names=F)`







