---
title: "ECCC 2016-19 Projects"
output:
  word_document:
    reference_docx: ../styles/GrantSummary.docx
---
**Last updated: `r format(Sys.Date(), "%B %e, %Y")`**

``` {r setup, echo=F, message=F, warning=F}
require(knitr)
opts_knit$set(root.dir = '..')
```

``` {r startup, echo=F, warning=F, message=F}
rm(list=ls())
require(ProjectTemplate)
load.project()
```

#### Projects with ECCC 2016-19 listed on PROJECTs page
``` {r, echo=T}
ecprojs <- data.frame(Project=projs$Project[grep("ECCC 2016-19", projs$Grants)], Projectpage="yes")
```

#### Projects assigned to an ECCC 2016-19 grant statement on GRANT INFO page
``` {r, echo=T}
promprojs <- data.frame(Project=bamGrantInfo$Project[bamGrantInfo$Grant %in% "ECCC 2016-19"], GRANTINFOpage="yes")

promclusprojs.tmp <- projs[projs$SubTheme %in% bamGrantInfo$ProjectCluster,]
promclusprojs.tmp <- promclusprojs.tmp[promclusprojs.tmp$Project.Status %in% c("ACTIVE", "STALLED", "ONGOING", "IDEA", "QUEUED"),]
promclusprojs <- data.frame(Project=promclusprojs.tmp$Project, GRANTINFOpage="yes")

promprojs <- rbind(promprojs, promclusprojs)
promprojs <- promprojs[!duplicated(promprojs),]
```

#### Table of both
``` {r echo=F}
myprojs <- merge(ecprojs, promprojs, by="Project", all=T)

myprojs <- myprojs[!duplicated(myprojs),]

myprojs <- myprojs[myprojs$Project != "",]
```

`r kable(myprojs)`

# ECCC 2016-19 grant "promises"
``` {r echo=F}
ecproms <- bamGrantInfo[bamGrantInfo$Grant %in% "ECCC 2016-19",]
ecproms$Heading.Lvl1 <- factor(ecproms$Heading.Lvl1)
ecpromss <- split(ecproms, ecproms$Heading.Lvl1.Order)

biglist <- lapply(ecpromss, function(x) {
  y <- x[order(x$Heading.Lvl2.Order),]
  data.frame(Project=y$Project, WorkplanText=y$GrantStatement, Deliverable=y$promisedDeliverable, Status=" ", Explanation=" ")
})
```

# `r unique(ecpromss[[1]]$Heading.Lvl1)`

`r kable(biglist[1], row.names=F)`


# `r unique(ecpromss[[2]]$Heading.Lvl1)`

`r kable(biglist[2], row.names=F)`

# `r unique(ecpromss[[3]]$Heading.Lvl1)`

`r kable(biglist[3], row.names=F)`

# `r unique(ecpromss[[4]]$Heading.Lvl1)`

`r kable(biglist[4], row.names=F)`

# `r unique(ecpromss[[5]]$Heading.Lvl1)`

`r kable(biglist[5], row.names=F)`

# `r unique(ecpromss[[6]]$Heading.Lvl1)`

`r kable(biglist[6], row.names=F)`

# `r unique(ecpromss[[7]]$Heading.Lvl1)`

`r kable(biglist[7], row.names=F)`

# `r unique(ecpromss[[8]]$Heading.Lvl1)`

`r kable(biglist[8], row.names=F)`

# `r unique(ecpromss[[9]]$Heading.Lvl1)`

`r kable(biglist[9], row.names=F)`

# `r unique(ecpromss[[10]]$Heading.Lvl1)`

`r kable(biglist[10], row.names=F)`


# Progress Updates on Each Project

``` {r}
updates <- ProjectUpdates[order(ProjectUpdates$Project, ProjectUpdates$UpdateDate),]
updates <- updates[c("Project", "UpdateDate", "TeamMember", "Question", "Update")]
updates <- merge(myprojs, updates, by="Project", all.x=T)
updates <- updates[c("Project", "UpdateDate", "Question", "Update", "TeamMember")]
```

`r kable(updates, row.names=F)`

