---
title: "2017 BAM Workplan"
author: "Overview by Priority"
output:
  word_document:
    reference_docx: ../styles/Overview.docx
---
**Last updated: `r format(Sys.Date(), "%B %e, %Y")`**

``` {r setup, echo=F, message=F, warning=F}
require(knitr)
opts_knit$set(root.dir = '..')
```

``` {r startup, echo=F, warning=F, message=F}
rm(list=ls())
require(ProjectTemplate)
load.project()
```

``` {r clean.status.priority.class, echo=F}
projs2 <- projs
#projs2 <- projs[! projs$PriorityClass.Project %in% c("Abandoned", "Complete"),]

projs2$Urgency.Priority.Status <- as.factor(paste(projs2$Project.Urgency, projs2$PriorityClass.Project, projs2$Project.Status, sep="."))
statprileg <- merge(projs2["Urgency.Priority.Status"],lookup.urgency.priority.status[c("Urgency.Priority.Status", "Order", "OverallStatus")], by="Urgency.Priority.Status", all.x=T)
statprileg <- statprileg[!duplicated(statprileg[c("OverallStatus")]),]
statprileg <- statprileg[order(statprileg$Order),]
statprileg$OverallStatus <- factor(statprileg$OverallStatus, levels=statprileg$OverallStatus) # sets the order to be presented in

projs2 <- merge(projs2, statprileg[c("Urgency.Priority.Status", "OverallStatus")], by="Urgency.Priority.Status", all.x=T) # adds OverallStatus name instead of full urgencyprioritystatus oen
```

``` {r eval=T, echo=F}
x <- split(projs2, projs2$OverallStatus)

projsum <- lapply(1:length(x), function(i) {
  z <- x[[i]]
  y <- data.frame(z[z$Project != "",])
  y <- y[!is.na(y[1]),]
  y <- y[order(y$Proj.Deadline),] # sorts projects by deadline, within a priority class
  #colnames(y)[1] <-names(x)[i]
  rownames(y) <- 1:nrow(y)
  a <- y[,c(1,3,7,5,6)]
  b <- c(StatusPriorityClass=names(x)[i],NumProjects=length(unique(y$Project)), NumClusters=length(unique(y$SubTheme)))
  list(a, b)
})
names(projsum) <- names(x)

proj.count <- as.data.frame(do.call(rbind, lapply(projsum, function(x) {
  x[[2]]
})))

forprinting <- lapply(projsum, function(x) {
  x[[1]]
})
```

# Introduction

This summary provides an overview of all projects currently on our workplan (i.e., in SharePoint).

Tables list projects and project clusters based on their priority and expected completion, with the following categories:

`r kable(proj.count, row.names=F)`

Priorities were assigned manually by Nicole into a SharePoint table based on discussion with Steering Committee and other team members throughout 2016 and at November 23 mini-workplanning meeting. 

If you're unclear what a given project or project cluster entails, there's a list at the end of the document. 

# Workplan Summary
### 1. `r names(forprinting)[1]`

`r kable(forprinting[[1]])`
<br> <br>

### 2. `r names(forprinting)[2]`
`r kable(forprinting[[2]])`
<br> <br>

### 3. `r names(forprinting)[3]`
`r kable(forprinting[[3]])`
<br> <br>

### 4. `r names(forprinting)[4]`
`r kable(forprinting[[4]])`
<br> <br>

### 5. `r names(forprinting)[5]`
`r kable(forprinting[[5]])`
<br> <br>

### 6. `r names(forprinting)[6]`
`r kable(forprinting[[6]])`
<br> <br>

### 7. `r names(forprinting)[7]`
`r kable(forprinting[[7]])`
<br> <br>

### 8. `r names(forprinting)[8]`
`r kable(forprinting[[8]])`
<br> <br>

### 9. `r names(forprinting)[9]`
`r kable(forprinting[[9]])`
<br> <br>

### 10. `r names(forprinting)[10]`
`r kable(forprinting[[10]])`
<br> <br>

### 11. `r names(forprinting)[11]`
`r kable(forprinting[[11]])`
<br> <br>

## Projects & project clusters requiring ranking
``` {r which.projs.clusters.are.unranked, echo=F, eval=F}
## Table of all projects and subthemes from the projs table
allpsdf <- projs[c("SubTheme", "Project")]
allpsdf <- allpsdf[!allpsdf$SubTheme == "",]
allpsdf <- allpsdf[!is.na(allpsdf$SubTheme),]
allpsdf$Project <- as.character(allpsdf$Project)

# remove subthemes that were classed (i.e., in the pris table)
sth.classed <- unique(as.character(pris$SubTheme))
pcdf.stunclassed <- allpsdf[!allpsdf$SubTheme %in% sth.classed,] #only unclassed subthemes
pcdf.stunclassed <- pcdf.stunclassed[!duplicated(pcdf.stunclassed),]

# identify projects in subthemes that were unclassed
p.unclassed <- as.character(pcdf.stunclassed$Project)

# remove projects that were classed
projs.classed <- unique(as.character(pris$Project))
p.unclassed <- p.unclassed[!p.unclassed %in% projs.classed] # projects that weren't directly classed or classed via subtheme.

# remove projects that aren't active
inactive.projs <- unique(as.character(projs$Project[projs$Project.Status %in% c("ABANDONED", "MERGED", "MORPHED", "NOT BAM", "COMPLETE")]))
p.unclassed.active <- p.unclassed[!p.unclassed %in% inactive.projs]

# left with a table of unclassed projects
```

``` {r print.table, echo=F, eval=F}
kable(data.frame(NeedsDecision=p.unclassed.active), row.names=T)
```

# Project and Project Cluster Objectives
``` {r echo=F}
allproj <- projs[projs$Project.Status %in% c("COMPLETE", "ACTIVE", "STALLED", "NOT BAM", "QUEUED", "IDEA", "PENDING"), c("Project", "Project.Objective", "SubTheme", "Cluster.Rationale", "Cluster.Goal")]
pcdf <- data.frame(Project.or.Cluster=c(as.character(allproj$Project), as.character(allproj$SubTheme)), Objective=c(as.character(allproj$Project.Objective), as.character(allproj$SubTheme.Goal)))
pcdf <- pcdf[order(pcdf$Project.or.Cluster),]
pcdf <- pcdf[!duplicated(pcdf),]
kable(pcdf, row.names=F)
```
