---
title: "Boreal Avian Modelling Project Work Plan"
author: "SAR Critical Habitat Identification (SAR-CH ID)"
date: "February 2017 - March 2019"
output:
  word_document:
    reference_docx: ../styles/SAR-CHWorkplan.docx
---

**Last updated: `r format(Sys.Date(), "%B %e, %Y")`**

## Purpose of this document

This document summarizes all activities proposed as part of BAM's SAR-CH work. It reflects activities:

* outlined in the proposed workplans for BAM's 2014-17 ECCC Contribution Agreement
* outlined in the proposed workplans for BAM's 2016-19 ECCC Contribution Agreement 
* identified through additional discussion within the BAM team or with ECCC staff
* proposed in answer to gaps identified in the schedule of studies


``` {r setup, echo=F, message=F, warning=F}
require(knitr)
opts_knit$set(root.dir = '..')
```

``` {r startup, echo=F, warning=F, message=F}
rm(list=ls())
require(ProjectTemplate)
load.project()
```

# Proposed Activities and Links to Schedule of Studies

``` {r, echo=F}
projs.sm <- projs[c("Milestone", "Project", "Lead", "Team.Initials", "TaskStatus", "Proj.Deadline", "AssignedTo", "AssignedToFirstname", "Task.Deadline")]
colnames(projs.sm)[1] <- "Task"

projs.sm$AssignedTo <- paste(projs.sm$AssignedToFirstname, projs.sm$AssignedTo, sep=" ")

sumtab <- merge(Workplanning.SAR.CH, projs.sm, by="Task", all.x=T)
projlevs <- data.frame(Project=sumtab$Proj_Clean, Order=sumtab$Order_ProjClean)
sumtab <- sumtab[order(sumtab$Order_ProjClean, sumtab$Order_Ta),]

sumtab <- data.frame(Project=as.character(sumtab$Proj_Clean), Task=sumtab$Task, SoS.Link=as.character(sumtab$SoS_RS), DetailedRationale=sumtab$Rationale, Responsible=sumtab$AssignedTo, Timeline=sumtab$Task.Deadline, TaskStatus=sumtab$TaskStatus, Notes=sumtab$Notes, Purpose=sumtab$Purpose_proj)

sumtab$Timeline <- as.character(sumtab$Timeline)
sumtab$Timeline[is.na(sumtab$Timeline)] <- ""
sumtab <- sumtab[sumtab$Project != "",]

sumtab$Project <- as.character(sumtab$Project)
```

``` {r fix.proj.order1, echo=F}
#Orders as indicated by project and task order indicators in SAR-ch workplan table
projlevs <- projlevs[!duplicated(projlevs$Project),]
projlevs <- projlevs[order(projlevs$Order),]

sumtab$Project <- factor(sumtab$Project, levels=projlevs$Project)
```

``` {r split.by.projclean, echo=F}
sumtabs <- split(sumtab, sumtab$Project)
sumtabs <- sumtabs[-which(names(sumtabs) == "")]
```

``` {r create.proj.datasets1, echo=F, eval=T}
proj.lvls <- 1:length(names(sumtabs))
```

``` {r, echo=F, eval=T}
src1 <- lapply(proj.lvls, function(proj.num) {
  knit_expand("scripts/SAR-CHWorkplan.lvl2.1.Rmd")
  })
```

Activities are roughly in the order they should be done, which aligns somewhat with the Schedule of Studies. Additional details follow this list of major activities:

`r knit(text=paste("* ", paste(names(sumtabs), collapse=" \n * "), sep=""))`



`r knit(text = unlist(src1))`


``` {r create.master.table, echo=F}
# Subset projects table for those Projects listed in the SAR-ch workplan table
sarproj <- projs[projs$Project %in% Workplanning.SAR.CH$Project,]

# Subset Projects table for key columns
sarproj <- sarproj[c("Project", "Project.Objective", "Lead", "Proj.Deadline", "Project.Status")]
sarproj$Proj.Deadline <- as.character(sarproj$Proj.Deadline)
sarproj$Proj.Deadline[is.na(sarproj$Proj.Deadline)] <- ""

#Take grant statements from grants table for projects listed in SAR workplan table
sarproj2 <- merge(sarproj, bamGrantInfo, by="Project", all.x=T)

#Take tasks for each project in the SAR-CH workplan table
sartask <- projs[projs$Milestone %in% Workplanning.SAR.CH$Task,]
sartask <- sartask[c("Milestone", "Task.Deadline", "AssignedToFirstname", "AssignedTo", "Project")]
colnames(sartask)[1] <- "Task"

# create master table of all projs and tasks
sarproj2$Project <- as.character(sarproj2$Project)
Workplanning.SAR.CH$Project <- as.character(Workplanning.SAR.CH$Project)
master <- merge(sarproj2, Workplanning.SAR.CH, by="Project", all=T)

write.table(master, "TmpCHworkplan.csv", sep=",", row.names = F, col.names = T)
#kable(master, row.names=F)
```

``` {r fix.proj.order, echo=F}
#Orders as indicated by project and task order indicators in SAR-ch workplan table
master <- master[master$Project != "",]

projlevs <- data.frame(Project=master$Project, Order=master$Order_Pr)
projlevs <- projlevs[!duplicated(projlevs$Project),]
projlevs <- projlevs[order(projlevs$Order),]

master$Project <- factor(master$Project, levels=projlevs$Project)
```

``` {r split.by.project, echo=F}
masters <- split(master, master$Project)
```

``` {r create.proj.datasets, echo=F, eval=T}
proj.lvls <- 1:length(names(masters))
```

``` {r, echo=F, eval=T}
src <- lapply(proj.lvls, function(proj.num) {
  knit_expand("scripts/SAR-CHWorkplan.lvl2.Rmd")
  })
```


``` {r eval=F, echo=F}
# Section 2. Rationale for each of the proposed activities

`r kable(sumtab[c("Task", "Rationale", "SoS.Link")])`


# Section 3. Detailed Project Descriptions

`r knit(text = unlist(src))`
```

## Schedule of Studies

`r kable(SoS, row.names=F)`